Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-03-01 vertical-thermal-review.Rmd
redo word count
@NidhiVinod , I just redid a careful word count using Word on my Mac, and it's much higher than what we had, matching what Holly said. I think you did the most recent one, but I know I did some word counts on the first submission that agreed with what you were getting -- or at least so I thought. But Holly is right that we're way over. How did we get so far off with the word count?

Text | word count | other | n
---|---|-----|--------------------
Total word count (excluding summary, references and legends) | 	9495 |	No. of figures | 	6 (all colour)
Summary|  	200 | 	No. of Tables | 	2  
Introduction|	393 |	No of Supporting Information files | 	6
Review of vertical gradients |	6374	||	 
Implications |	2408	 ||
Conclusions |	276	||
Acknowledgments | 43	||

>>>>

Text | word count | other | n
---|---|-----|--------------------
Total word count (excluding summary, references and legends) | 	11854 |	No. of figures | 	6 (all colour)
Summary|  	200 | 	No. of Tables | 	2  
Introduction|	498 |	No of Supporting Information files | 	6
Review of vertical gradients |	8192	||	 
Implications |	2842	 ||
Conclusions |	278	||
Acknowledgments | 44	||
